\textbf{Dimpho Mahoko} \\
	I am an aspiring software developer looking to gain new skills and develop those I already have. Notable skills include web development, fluency in Java, C++, JavaScript, PHP, HTMLand  NodeJS  \\ 
	 Below are my accomplishments worth mentioning in no particular order.
	\begin{itemize}
		\item Second place in the Standard Bank IT challenge finals in 2016. The task was to design and implement an application for Amazon's Echo (Alexa) that was financially relevant. \\
	
		\item Webmaster at Tuks FM from September 2016 till present. \\ 
			Responsibilities include maintaining the website and keeping it up to date. \\
			
		\item Mentor at The University of Pretoria EBIT Week for EBIT Marketing \\
			Responsibilities include database administration, website maintenance and all other admin related responsibilities like communication with parents whose children wish to attend EBIT Week. \\
			
		\item 2016 Retro Rabbit Rabbiteer program attendee \\
			The program was focused mainly on giving programming students an idea of how work in the industry is actually done. Notable technologies learnt include GitHub integration with team work and cloud computing and hosting. \\%I'll elaborate further
	\end{itemize}
	

\textbf{Jason van Hattum}\\
\textit{Team Leader}\\
    I am a motivated developer with a passion for application and web-app development. Technologies that I am fluent in include full-stack MEAN and LAMP development, Java, C++, Android, Python and Django. I have experience in project management, web-app development and Android application development. \\
    
    I enjoy experimenting in my free time, especially working on side projects on my Raspberry Pi and building Android applications. I also enjoy making graphical programs in WebGL. My hobbies also include reading, playing games, and fishing. \\
    
    \noindent
    Projects that I have worked on include:
    \begin{itemize}
        \item A web application for the University of Pretoria used for peer-review and team evaluation within major projects (Can be found \href{https://github.com/teampinocchio/pinocchio/wiki}{\underline{here}}.). Skills that I developed here include front-end languages such as HTML, CSS, and Javascript; Python and Django.
    
        \item A variety of Android applications as a freelancing developer, both front-end and back-end. Skills developed here include Android development, Google Firebase, interface design and NodeJS.
    \end{itemize}
    
    \noindent
	Accomplishments and work experience:
    \begin{itemize}
        \item A member of the Golden Key International Honors Society.
        \item A teaching assistant and tutor for multiple subjects since January 2016.
        \item Participated in the Standard Bank IT Challenge in 2016 and 2017; and ACM in 2016.
        % \item Passed AI
        % \item Got destroyed in the Digital Gaming League, Dota division.
    \end{itemize}

\textbf{Kyle Erwin}\\
	Currently studying a BSc Computer science. I'm a well rounded programmer with many skills in many languages. My passion lies in artificial intelligence and creating applications with an intuitive design. I'm a harder worker that is known to be ``on top of things`` by my peers. \\ 

	I've worked in many leader positions and understand the importance of synergy in a team. Most noteworthy, I was apart of the TukVillage residence committee and the graphic desiner for all of the events (2015 - 2016). I launched a web development company, \href{www.unhinged.co.za}{\underline{unhinged.co.za}}, with team member Keagan Ferrett. My work has also extended to app development and partnerships with small startup companies.\\

	In my free time I often find myself programming on personal projects, coming up with new concepts and focusing my time on perfection my artificial intelligence skills. 

	\noindent
	More about me and my skills:
    \begin{itemize}
        \item Up-to-date with all the latest design trends.
        \item Used applications such as google analytics, webmaster and google trends. 
        \item Written many C++ tutorials for beginner programmers
        \item Business skills and working with clients. 
        \item An understanding of scala, a programming language great for AI. 
    \end{itemize}
    
\textbf{Joshua Cilliers}\\
I am currently in my final year of studying a BSc Computer Science and hoping to continue on to Honours. I'm an aspiring programmer with a broad set of skills that go beyond programming. I hope to move further into the development of complex systems, on both the front and back end of development. I enjoy broadening my experiences as much as possible and am always eager to attempt new projects and to learn more while doing so.\\

My programming experience includes being fully fluent in C++, Java, LAMP and MEAN stack development, and Python. I have also worked on projects for iOS and Android and have experience with tools and frameworks such as Ionic.\\

I offer freelance web development and social media marketing services in my free time when I'm not pursuing my own hobbies and interests.\\

My current personal hobbie is attempting to learn about the development process in Unreal Engine 4 so that I can contribute to the open-source Unreal Tournament project.\\

My other hobbies include photography, photo-editing and film-editing, tinkering with hardware, game development (specifically level and systems design), and reading and writing.\\

My skill-set and interests include:
\begin{itemize}

        \item A focus on developing well rounded systems.
        
        \item Experience in designing the front-end of websites and a handful of systems.
        
        \item Experience in developing for the back-end of systems.
        
        \item A willingness to learn new languages and technologies.
        
    \end{itemize}

\textbf{Keegan Ferrett}\\
\textit{Project Manager}\\
    Currently in my final year of studying BSc Computer Science. I am an aspiring software developer with a love for mathematics and problem solving. I am a passionate programmer who is excited to develop my skills and knowledge. I enjoy taking on leadership roles and pushing myself with exciting and large projects. \\

    I have launched a website designed and development business, \href{www.unhinged.co.za}{\underline{unhinged.co.za}}, with another team mate Kyle Erwin. My role in the business is mostly backend development and running the business's accounting, however our vision is to one day extend into larger, and more complex projects, which we hope with this give up the experience to do.\\

    During my free time I enjoy working on my Android app development skills, experimenting with pyshcical computing (skilled with using Raspberry Pis and Arduinos), as well as Competeing in various programming and problem solving contests. Some contests that I have completed are; Stanard Bank IT Challange 2016 and 2017, ACM 2016, and HackFu challenge 2016.\\

    \noindent
    Below are some of my passions and interests:
    \begin{itemize}
        \item Android App Development
        \item Mathematics
        \item Compiler Design and Construction
        \item Physical Computing and Electronic Engineering
        \item Computer Networks and Security
    \end{itemize}

\end{document}
